### 2013-07-29 Tex/chapters/model.tex
Korrekturen, Ergänzungen, Umformulierungen
Beschreibung des Torus geändert

    lives on the surface of a torus like in fig. \ref{fig:torusRNG}.

@@

            itself. Also the shades are of course only a guide to the eye.

@@

    is studied for constant \(J\) on the Delaunay triangulation\cite{Janke1994}.\\

>>>>

    lives on the surface of a torus as pictured in fig. \ref{fig:torusRNG}.

@@

            itself. Hence, the torus represents the geometry of the model
            not perfectly, but gives very quick the right idea.
            %Also the shades are of course only a guide to the eye.

@@

    is already studied for constant \(J\) on the Delaunay triangulation
    in \cite{Janke1994}.\\
